Positivity-Preserving Adaptive Runge--Kutta Methods

### 2021-03-04 nusslein_vsrp/latex/response_to_reviewers.tex

    \item \emph{%
    After formula (5.2) ``...In Figure 4a the results for $\Delta t = 0.015$
    are plotted for different time steps...'' should be ``...In Figure 4a the
    results for $\Delta t = 0.015$ are plotted for different values of time $t$...''
    }

    We fixed this sentence [line~\ref{line:time-vs-dt}].

    \item \emph{%
    Figure 5, about the non-stiff problem with fixed stepsize, is quite interesting
    and gives information about the convergence of the adapted mehtod. For
    $\Delta t = 0.0082$ the unaltered method leads to positive solutions. For
    $\Delta t = 0.015$ the original method leads to negative values in the
    interval $[0, 0.375]$ and the weights are altered by solving an LP problem.
    Is this extra time consuming a significant cost or could it be an economical
    alternative to using excessively small step sizes? A further explanation
    about this issue should be added.
    }

    We investigated this and added a remark at the end of Section 5.1, explaining
    that the LP approach is more expensive for the problem in Section 5.1 but more
    economical for the problem in Section 5.2.  One should not extrapolate too
    much from these results, but our approach would be even
    more efficient for more challenging problems where evaluation of $f$ or
    solution of the stage equations is more costly.  [line~\ref{line:cost}]

### 2021-03-04 nusslein_vsrp/latex/overview.tex
update references
Mention efficiency for stiff problem.

\linelabel{line:cost}\revA{
It is natural to ask whether the adaptation of the weights through the algorithm proposed
here is more efficient than simply using a smaller step size.  For this problem that can
be discretized explicitly with a right-hand-side that is relatively cheap to evaluate,
using a smaller step size is
generally more efficient, at least with the current un-optimized implementation of the LP
solution.  For problems where implicit time integration is necessary, or with a more computationally
expensive derivative evaluation, the LP approach may be more efficient, especially if
the implementation were optimized.  This kind of optimization is the subject of future work.
}

>>>>

\linelabel{line:cost}\revA{
It is natural to ask whether the adaptation of the weights through the algorithm proposed
here is more efficient than simply using a smaller step size.  For this problem that can
be discretized explicitly with a right-hand-side that is relatively cheap to evaluate,
using a smaller step size is
generally more efficient, at least with the current un-optimized implementation of the LP
solution.  For the problem considered in the next section, where an implicit
integrator is used, it is more efficient to maintain positivity with our proposed
approach instead of reducing the step size.
Adaptation of the weights could be made even more efficient with
an optimized implementation of the LP setup and solve; this is the subject of future work.
}
